resistanceModelNotesAndy

### 2015-03-18 resistanceModelNotesAndy.Rmd
progress notes

listFunctions("malaria_code_fromBeth.R")
```

@@

**17/3/15** weds in liverpool 8.45-

@@

### TO DO  
1. add myself as maintainer in DESCRIPTION
1. sort location in package of "input.parameters.csv" functions should be able to run without it
1. check out the part about running sequential insecticide scenarios
1. start to write script to run sensitivity analysis, does it want to work by creating a large input.csv file, or by setting input object directly.
1. spend some time developing my understanding of how the model works
1. submit tilde bug report
1. later, structure as R package, maybe move to a new github repo
1. re-look at R popgen packages when I've got more of a handle on what we are doing.

>>>>

#listFunctions("C:\\Dropbox\\Ian and Andy\\andy\\malaria\\Beth code\\malaria_code_beth.r")
```

@@

**17/3/15** weds in liverpool 8.30-6 9.5hrs

@@

package does build now

potential refactoring of code, if i think carefully, using arrays I should be able to replace this :
```
    if(calibration==103){		## no selection calibration
        ## male
        # SS1
        fs.m.SS1SS2 <- f.m.SS1SS2
        fs.m.SS1RS2 <- f.m.SS1RS2
        fs.m.SS1RR2 <- f.m.SS1RR2
        # RS1
        fs.m.RS1SS2 <- f.m.RS1SS2 
        fs.m.RS1RS2_cis <- f.m.RS1RS2_cis
        fs.m.RS1RS2_trans <- f.m.RS1RS2_trans
        fs.m.RS1RR2 <- f.m.RS1RR2
        # RR2 
        fs.m.RR1SS2 <- f.m.RR1SS2
        fs.m.RR1RS2 <- f.m.RR1RS2
        fs.m.RR1RR2 <- f.m.RR1RR2

        ## female
        # SS1
        fs.f.SS1SS2 <- f.f.SS1SS2
        fs.f.SS1RS2 <- f.f.SS1RS2
        fs.f.SS1RR2 <- f.f.SS1RR2
        # RS1
        fs.f.RS1SS2 <- f.f.RS1SS2 
        fs.f.RS1RS2_cis <- f.f.RS1RS2_cis
        fs.f.RS1RS2_trans <- f.f.RS1RS2_trans
        fs.f.RS1RR2 <- f.f.RS1RR2
        # RR2 
        fs.f.RR1SS2 <- f.f.RR1SS2
        fs.f.RR1RS2 <- f.f.RR1RS2
        fs.f.RR1RR2 <- f.f.RR1RR2
```

with something like :
`fs <- f`

where arrays are set up as :
```{r}
#to create an array a[sex][locus1][locus2]
namesLoci <- c('SS','RS','RR')
locus1 <- paste0(namesLoci,'1')
locus2 <- paste0(namesLoci,'2')
sex <- c("F","M")

dimnames1 <- list( sex=sex, locus1=locus1, locus2=locus2 )
dim1 <- sapply(dimnames1, function(x) length(x))
a <- array(0,dim=dim1, dimnames=dimnames1)
a
length(a)
#to access one element
a['M','SS1','RR2']
#to check that males total 1
sum(a['M',,])
```

Just need to work out how best to deal with cis & trans.
This would be a less pleasing alternative
```{r}

namesLoci <- c('SS1SS2','SS1RS2','SS1RR2',
               'RS1SS2','RS1RS2','RS1RR2',
               'RR1SS2','RR1RS2','RR1RR2')

#adding cis & trans
namesLoci <- c('SS1SS2','SS1RS2','SS1RR2',
               'RS1SS2','RS1RS2cis','RS1RS2trans','RS1RR2',
               'RR1SS2','RR1RS2','RR1RR2')

sex <- c("F","M")

dimnames1 <- list( sex=sex, namesLoci=namesLoci )

dim1 <- sapply(dimnames1, function(x) length(x))
a <- array(0,dim=dim1, dimnames=dimnames1)
a
length(a)
#to access one element
a['M','SS1SS2']
#to check that males total 1
sum(a['M',])
str(a)
```

### TO DO  
1. add myself as maintainer in DESCRIPTION
1. sort licence in description
1. put back in checks for things that should sum to 1
1. edit runModel carefully
1. check whether functions can run without "input.parameters.csv" 
1. check out the part about running sequential insecticide scenarios
1. start to write script to run sensitivity analysis, does it want to work by creating a large input.csv file, or by setting input object directly.
1. spend some time developing my understanding of how the model works
1. submit tilde bug report
1. later, structure as R package, maybe move to a new github repo
1. re-look at R popgen packages when I've got more of a handle on what we are doing.
